---
title: "Final Project 2: Orthopedic Reimbursements in Illinois"
output: html_document
author: "Cathy Nguyen"
date: "2024-02-07"
code-fold: FALSE
---

The data set  compares Medicaid, Medicare, and commercial (Blue Cross Blue Shield) reimbursement rates for different orthopedic CPT codes. The data  outlines how much a physician would get reimbursed through different insurances for the same procedure.

The analysis in the report looks at the average reimbursements, and other descriptive statistics, for each insurance within orthopedics. It also compares Medicare as a function of Medicaid, in an attempt to examine their correlation.

``` {r, global-chunks, echo = FALSE, warning = FALSE, message = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```

```{r, load data, echo=FALSE, message=FALSE, warning=FALSE}
library(readxl)
data <-read_excel("~/data550/cptcodes.xlsx")
```

# Descriptive Analysis

## Tabular analysis

Characteristics, including the mean, maximum, and minimum reimbursement rates of the `r nrow(data)` different orthopedics CPT code rates for different insurance types in the state of Illinois are listed below.

```{r, table1}
readRDS(
  here::here("output/table.rds")
)
```

## Graphical analysis

Below we report a scatter plot of Medicare CPT reimbursement rates for different orthopedic procedures as a function of Medicaid. 

```{r, plot-data}
fig.align = "center"
out.width = "600px"
knitr::include_graphics(
 here::here("output/scatterplot.png"))
```